---
title: "Social network analysis demo"
author: "Adrienne Wood"
date: "03/27/2020"

output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    code_folding: hide
---

```{r set defaults,include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8) 
```

```{r load libraries,include=FALSE}
if(!require(pacman)) install.packages("pacman"); require(pacman)
p_load(igraph, RColorBrewer,lmSupport,knitr,DT)
```


# Social network of the class Wiki

### Load data...

```{r load data}
# read in the social network edges file
edges <-read.csv("wiki_edges.csv")
kable(edges, caption="All Wiki connections")

```

### Create an igraph network from the edges dataframe. 
"Directed" means we want to preserve information about whether a link was incoming or outgoing

```{r create network}
net <-graph_from_data_frame(edges,directed=T)

# modify a few properties of graph
E(net)$arrow.size <- 0.2
E(net)$width <- 0.5

```

## Graph the Wiki network
```{r graph}

# pick the network layout algorithm we'll use
coords <- layout.kamada.kawai(net)

# make a function to scale the vertex sizes
scalevals <- function(v, a, b) {v <- v-min(v) 
                                v <- v/max(v) 
                                v <- v * (b-a) 
                                v+a }

# set min and max node sizes
min_size_node = 4
max_size_node = 8

# scale node size according to node strength (weighted degree centrality)
nodesize_strength = scalevals(strength(net), min_size_node, max_size_node)

# plot
myPlot<-plot.igraph(net,
    vertex.size = nodesize_strength,
     edge.color="#00000088",

     edge.curved=.2,
    layout = coords)



```

## Graph the Wiki network without the Home vertex; detect communities 
```{r without home}

netNoHomeD <-delete_vertices(net, "Home")
netNoHome <- as.undirected(netNoHomeD, mode = c("collapse"))
# scale node size according to node strength (weighted degree centrality)
min_size_node=4
max_size_node=8
nodesize_strength = scalevals(strength(netNoHome), min_size_node, max_size_node)

coords <- layout.fruchterman.reingold(netNoHome)

#### identify communities of topics ####

# implement fast greedy modularity optimization algorithm 
# to find community structure
communities <- cluster_fast_greedy(netNoHome)

# assign community membership as vertex attribute 
V(netNoHome)$community <- communities$membership
commnunity_pal <- brewer.pal(max(V(netNoHome)$community),"Set3")

# plot, coloring nodes by community membership

plot.igraph(netNoHome,
    vertex.size = nodesize_strength,
    vertex.color = commnunity_pal[V(netNoHome)$community],
    edge.color="#00000088",
    edge.curved=.2,
    layout = coords)


```


# Describe the topics' network positions
```{r network descriptives}

indegreeCentrality<-igraph::degree(netNoHomeD,mode="in")
outdegreeCentrality<-igraph::degree(netNoHomeD,mode="out")
eigenvectorCentrality <- igraph::eigen_centrality(netNoHomeD,directed=T)$vector
betweennessCentrality <- igraph::betweenness(netNoHomeD, directed=T)
clusteringCoefficient <- igraph::transitivity(netNoHomeD,type="local",isolates="zero")
pagerank <- igraph::page_rank(netNoHomeD,directed=T)$vector
constraint <- igraph::constraint(netNoHomeD)
    
allScores <-cbind(indegreeCentrality,outdegreeCentrality,eigenvectorCentrality,betweennessCentrality,clusteringCoefficient,pagerank,constraint)
allScoresD <-data.frame(allScores)
allScoresD$topic <-rownames(allScoresD)
DT::datatable(allScoresD,caption="Network variables")
```

# Correlations between network variables
```{r correlations}
DT::datatable(cor(allScoresD[,1:7]),caption="Correlations")
```

# Communities
```{r communities}
# combine with communities info
commdf <-data.frame(topic=communities$names,community=communities$membership)

allScores <- join(allScoresD,commdf,by=c("topic"))
kable(communities[1:22])

```